\documentclass[11pt, a4paper, leqno]{article}
\usepackage{a4wide}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{float, afterpage, rotating, graphicx}
\usepackage{epstopdf}
\usepackage{longtable, booktabs, tabularx}
\usepackage{fancyvrb, moreverb, relsize}
\usepackage{eurosym, calc}
% \usepackage{chngcntr}
\usepackage{amsmath, amssymb, amsfonts, amsthm, bm}
\usepackage{caption}
\usepackage{mdwlist}
\usepackage{xfrac}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{minibox}
\usepackage{adjustbox}
\usepackage{comment}
% \usepackage{pdf14} % Enable for Manuscriptcentral -- can't handle pdf 1.5
% \usepackage{endfloat} % Enable to move tables / figures to the end. Useful for some submissions.


\usepackage[
    natbib=true,
    bibencoding=inputenc,
    bibstyle=authoryear-ibid,
    citestyle=authoryear-comp,
    maxcitenames=3,
    maxbibnames=10,
    useprefix=false,
    sortcites=true,
    backend=biber
]{biblatex}
\AtBeginDocument{\toggletrue{blx@useprefix}}
\AtBeginBibliography{\togglefalse{blx@useprefix}}
\setlength{\bibitemsep}{1.5ex}
\addbibresource{refs.bib}





\usepackage[unicode=true]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    anchorcolor=black,
    citecolor=black,
    filecolor=black,
    menucolor=black,
    runcolor=black,
    urlcolor=black
}


\widowpenalty=10000
\clubpenalty=10000

\setlength{\parskip}{1ex}
\setlength{\parindent}{0ex}
\setstretch{1.5}


\begin{document}

\title{covid-19 Mobility\thanks{Bahar Coskun, Timo Haller, Anto Marcinkovic, Universitaet Bonn. Email: \href{mailto:s6bacosk@uni-bonn.de, s6tohall@uni-bonn.de, s3anmarc@uni-bonn.de}{\nolinkurl{s6bacosk [at] uni-bonn [dot] de, s6tohall [at] uni-bonn [dot] de, s3anmarc [at] uni-bonn [dot] de}}.}}

\author{Bahar Coskun, Timo Haller, Anto Marcinkovic}

\date{
    {\bf Preliminary -- please do not quote}
    \\[1ex]
    \today
}

\maketitle


\begin{abstract}
    Some abstract here.
\end{abstract}
\clearpage

\tableofcontents
\clearpage

\section{Introduction} % (fold)
\label{sec:introduction}

If you are using this template, please cite this item from the references: \citet{GaudeckerEconProjectTemplates}

\newpage

\section{Regression}

This short paragraph provides an explanation on our regression analysis.
In our analysis we want to identify the effect of lockdown fatigue, which means people reduce their mobility less after a long lockdown history.
Therefore we estimate the following regression model:


$\textit{mobility}_{t} = \beta_{0} + \beta_{1} \textit{LD1}_{t} + \beta_{1} \textit{LD1}_{t} + \beta_{1} \textit{LD1}_{t} \times + \textit{LD1\_Duration}_{t} + \beta_{2} \textit{LD2}_{t} \times \textit{LD2\_Duration}_{t} + \beta_{5} + \gamma \mathbf{X} + \epsilon_{i}$

whereby $\textit{LD1}_{t} $ and $\textit{LD2}_{t}$ denote the second and first lockdown. The variable $\textit{LD1\_Duration}_{t}$ is the duration of the first lockdown (equivalently for $\textit{LD1\_Duration}_{t}$). Furthermore, $\textit{stringency}$ controls for the stringency index. Additional control variables, in particular the infection case number, are summarized in the $\mathbf{X}$ vector. \\
The marginal effects of interest are $\beta_{2}$ and $\beta_{3}$. We expect $\beta_{3}$ to be positive and $\beta_{2}$ to be zero or even negative. The following section shows the tables for different mobility measures as dependent variables.





\newpage

\begin{table}
	\centering
	\caption{Lockdown Fatigue for Workplace Mobility (7 Days Moving Average)}
	\scalebox{0.8}{%
	\input{../../bld/tables/table_regression_workplaces_avg_7d.tex}
}

\end{table}


\newpage

\begin{table}
	\centering
	\caption{Lockdown Fatigue for Transit Station Mobility (7 Days Moving Average)}
	\scalebox{0.8}{%
		\input{../../bld/tables/table_regression_transit_stations_avg_7d.tex}
	}
\end{table}

\newpage

\begin{table}
	\centering
	\caption{Lockdown Fatigue for Retail and Recreation Mobility (7 Days Moving Average)}
	\scalebox{0.8}{%
		\input{../../bld/tables/table_regression_retail_and_recreation_avg_7d.tex}
	}
\end{table}

\newpage

\begin{table}
	\centering
	\caption{Lockdown Fatigue for Grocery and Pharmacy Mobility (7 Days Moving Average)}
	\scalebox{0.8}{%
		\input{../../bld/tables/table_regression_grocery_and_pharmacy_avg_7d.tex}
	}
\end{table}

\newpage

\begin{table}
	\centering
	\caption{Lockdown Fatigue for Residential Mobility (7 Days Moving Average)}
	\scalebox{0.8}{%
		\input{../../bld/tables/table_regression_residential_avg_7d.tex}
	}
\end{table}

\clearpage

\setstretch{1}
\printbibliography
\setstretch{1.5}




% \appendix

% The chngctr package is needed for the following lines.
% \counterwithin{table}{section}
% \counterwithin{figure}{section}

\end{document}
